---
title: "Google VM Placement"
author: 
  - Stenio Araujo
  - Brendha Cruz
institute: "Metodologia Cientifica 2016.2 | UFCG"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(knitr)
library(readr)
library(resample)
library(stringr)
```

# Factors and Dependet Variables
## Factors
Factor: Algorithm  
Levels:  

- Best Fit-based (BF)
- First Fit (FF)
- Worst Fit-based (WF)

Factor: Available resource on servers  
Levels:  

- 5.0 CPU and 9.6 MEM
- 2.5 CPU and 4.8 MEM
- 1.0 CPU and 1.9 MEM

Factor: Requested resource by VM  
Levels:  

- Normal
- Large

## Dependent Variables
- Denied requests (When it is not possible to allocate a VM request)
- Fragmentation

# Reading the data
```{r message=FALSE}
experiment_results = read_csv("../experiment_results.csv")
```

# Plot for the depenent variable Denied Requests
```{r fig.width=10}
algorithm =
  ggplot(experiment_results,
         aes(algorithm, number_of_rejected_vms)) +
  geom_point() +
  geom_text(aes(label=number_of_rejected_vms), hjust=-0.2, vjust=.5) +
  theme_grey(base_size = 18) +
  xlab("Algoritimo") + ylab("Número de requisições negadas")
algorithm

cpu_mem = experiment_results %>%
  mutate(cpu_mem = paste(max_cpu_per_bin, "CPU", max_mem_per_bin, "MEM"))
available_resources =
  ggplot(cpu_mem,
         aes(cpu_mem, number_of_rejected_vms)) +
  geom_point() +
  geom_text(aes(label=number_of_rejected_vms),
            hjust=-0.2, vjust=.5, check_overlap = TRUE) +
  theme_grey(base_size = 18) +
  xlab("Tamanho da Máquina Servidor") + ylab("Número de requisições negadas")
available_resources

requested_resource =
  ggplot(experiment_results,
         aes(vm_size, number_of_rejected_vms)) +
  geom_point() +
  geom_text(aes(label=number_of_rejected_vms),
            hjust=-0.2, vjust=.5, check_overlap = TRUE) +
  theme_grey(base_size = 18) +
  xlab("Tamanho da VM") + ylab("Número de requisições negadas")
requested_resource
```

# Plot for the depenent variable Fragmentation
```{r fig.width=10}
avg_frag = experiment_results %>%
  mutate(avg_fragmentation = fragmentation_cpu/2.0 + fragmentation_mem/2.0)

algorithm =
  ggplot(avg_frag,
         aes(algorithm, avg_fragmentation)) +
  geom_point() +
  geom_text(aes(label=avg_fragmentation),
            hjust=-0.2, vjust=.5, check_overlap = TRUE) +
  theme_grey(base_size = 18) +
  xlab("Algoritimo") + ylab("Fragmentação média")
algorithm

cpu_mem = avg_frag %>%
  mutate(cpu_mem = paste(max_cpu_per_bin, "CPU", max_mem_per_bin, "MEM"))
available_resources =
  ggplot(cpu_mem,
         aes(cpu_mem, avg_fragmentation)) +
  geom_point() +
  geom_text(aes(label=avg_fragmentation),
            hjust=-0.2, vjust=.5, check_overlap = TRUE) +
  theme_grey(base_size = 18) +
  xlab("Tamanho da Máquina Servidor") + ylab("Fragmentação média")
available_resources

requested_resource =
  ggplot(avg_frag,
         aes(vm_size, avg_fragmentation)) +
  geom_point() +
  geom_text(aes(label=avg_fragmentation),
            hjust=-0.2, vjust=.5, check_overlap = TRUE) +
  theme_grey(base_size = 18) +
  xlab("Tamanho da VM") + ylab("Fragmentação média")
requested_resource
```
